---
title: 'DS 202 - Lab 2: Team'
author: "Connor Carpenter"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco)
```

## 1.) 1852

## 2.) 
```{r}
library(ggplot2)
ggplot(choco, aes(x=Review.Date))+ 
  geom_bar(fill = "blue", colour = "black")+
  theme_bw()+
  theme(axis.title.y = element_text(size = rel(1.4)),
        axis.title.x = element_text(size = rel(1.4)),
        axis.text.x = element_text(size = rel(1.6)),
        axis.text.y = element_text(size = rel(1.6)),
        plot.title = element_text(hjust=0.5, size = rel(2)))+
  labs(x = "Review Date",
       y = "Count",
       title = "Count of Reviews by Year")+ 
  ylim(0, 300)
```

**Reviews vary by year**

## 3.)

```{r}
summary(choco)
```
### USA(787), France(158), Canada(132)

## 4.)

- Is there a correlation between each individual company, the countries that each company uses, and the respective rating?
- Is there a correlation between Review Date and the Rating?
- Is there a correlation between the cocoa percentage and the country of origin?
- Is there a correlation between the cocoa percentage and the company of origin?

## 5.)

### Is there a correlation between the cocoa percentage and the company of origin?

```{r}
choco$Company.Index <- match(choco$Company, unique(choco$Company))
plot(choco$Company.Index, choco$Cocoa.Pct)
```

There's a suspiciously high number of chocolate bars made with 25% cocoa among all companies

But otherwise there isn't really much of a relationship.

## 6.)
